ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-09-29 rebuttal.tex

\begin{reviewer}
    %
    ``For example, where PrIMe uses internal bibliographic references, ReSpecTh adds a field for
    typical bibliographic data.''

    I suggest the following extension:

    ``For example, where PrIMe uses internal bibliographic references, ReSpecTh adds a field for
    typical bibliographic data, including the DOI of the cited arecicle. Each datafile has a unique
    own DOI and unique URL address.
    [\url{http://respecth.chem.elte.hu/respecth/reac/CombustionData.php}]''. Also species can be
    identified by InCHI or SMILES.
    %
\end{reviewer}

\begin{response}
    %
    We have incorporated these modifications into the suggested paragraph, although we have modified
    the format slightly to better fit the flow of the text.
    %
\end{response}

@@

\begin{reviewer}
    %
    ``The ReSpecTh standard also provides machine-readable formats for describing ignition
    experiments, including a field for the definition of autoignition and the ability to specify
    facility-specific effects.''

    Modified text:

    ``The ReSpecTh standard provides formats that are both human and machine-readable for describing
    ignition experiments, including a field for the definition of autoignition and the ability to
    specify facility-specific effects. Also, it describes PSR and flow reactor speciation data,
    burner stabilized flame speciation data and burning velocity data.''
    %
\end{reviewer}

\begin{response}
    %
    We have incorporated most of the recommended text in our revision. However, we did not add
    ``human-readable'', consistent with the definition used throughout (i.e., the XML file is more
    verbose and less easily understood).
    %
\end{response}

### 2017-09-29 rebuttal.tex

\begin{response}
    %
    We have incorporated most of the recommended text in our revision. However, we did not add
    ``human-readable'', consistent with the definition used throughout (i.e., the XML file is more
    verbose and less easily understood).
    %
\end{response}

\begin{reviewer}
    %
    ``However, ReSpecTh experimental files are another XML-based format, and, as such, suffer from
    the same usability issues as PrIMe.''

    I think that the limits of an XML database is set by the actual set of tags and not the format.
    %
\end{reviewer}

\begin{response}
    %
    By ``usability'' of a format, we mean whether files are easily usable and understandable by
    people, rather than the technical limitations of a format. We have changed the word
    ``usability'' to ``readability'' to emphasize this.
    %
\end{response}

### 2017-09-29 rebuttal.tex

\begin{reviewer}
    %
    ``Moreover, the standard remains closed, requiring potential users to register with the
    standard's authors to access the specification and the growing database.''

    I suggest instead:

    ``Registration is open for everyone who provides a valid institutional e-mail address.''
    %
\end{reviewer}

\begin{response}
    %
    We have updated the text to reflect this information; however, we argue that requiring
    registration to view the specification and data limits the possibility of use of the standard
    and differs from the openness that we are advocating, where the specification and data files are
    open for anyone to view, with or without registration.
    %
\end{response}

### 2017-09-30 rebuttal.tex

\begin{response}
    We added the suggested text and reference.
\end{response}

\begin{reviewer}
    %
    ``type (required, string): How ignition delay was measured;''

    The options described here is a very limited subset of the ignition delay time definitions used
    in experimental articles. For example, backward or forward interpolated values of a measured
    quantity are further possibilities.
    %
\end{reviewer}

\begin{response}
    %
    We have implemented an option for baseline extrapolation of the slope. We have added the
    description of this ignition type to the mentioned portion of the manuscript. To our knowledge,
    the options now supported represent all of the common methods of specifying the ignition delay
    in rapid compression machine and shock tube experiments.
    %
\end{response}

### 2017-09-30 pyked.tex
Update response for #11. Change usability to readability to clarify
Work on #14.
I made a PR (pr-omethe-us/PyKED#77) to close the related issue
(pr-omethe-us/PyKED#71). This should address the reviewer's comment.

However, ReSpecTh experimental files are another
XML-based format, and, as such, suffer from the same usability issues as PrIMe.
Moreover, the standard remains inaccessible to the public, requiring potential users
to register with the standard's authors using a valid institutional email address
to access the specification and the growing database.

@@

The second section of the file encodes the experimental data. The \ck{} file
describes these using a sequence of mappings, with the following information required
in each element of the sequence:
%
\begin{itemize}
    \item \yabox|temperature| (required, sequence): The temperature of the
    experiment, with units and optionally uncertainty
    \item \yabox|ignition-delay| (required, sequence): The ignition delay of the
    experiment, with units and optionally uncertainty
    \item \yabox|pressure| (required, sequence): The pressure of the experiment,
    with units and optionally uncertainty
    \item \yabox|composition| (required, mapping): The composition of the
    mixture in the experiment, described via a nested mapping with the fields
    \begin{itemize}
        \item \yabox|kind| (required, string): one of \yabox|mole fraction|, \yabox|mole percent|, or \yabox|mass fraction|
        \item \yabox|species|: sequence of mappings, with the fields
        \begin{itemize}
            \item \yabox|species-name| (required, string): The name of the species
            \item \yabox|amount| (required, sequence): The mole fraction or percent, or the mass fraction, optionally with uncertainty
            \item \yabox|InChI|, \yabox|SMILES|, \yabox|atomic-composition|, or
            \yabox|elemental-composition| (required, string or sequence): The InChI
            or SMILES string representing the molecule, or its atomic or elemental
            composition (\yabox|atomic-composition| and\\
            \yabox|elemental-composition| are synonyms) as a sequence
        \end{itemize}
    \end{itemize}
    \item \yabox|ignition-type| (required, mapping): The method used to detect
    ignition in the experiments. The required fields are
    \begin{itemize}
        \item \yabox|type| (required, string): How ignition delay was
        measured; one of \yabox|d/dt max| (indicates the ignition point was
        found at the maximum of the time derivative of the \yabox|target|),
        \yabox|max| or \yabox|min| (indicates the ignition point was at the
        maximum or minimum of the \yabox|target|), or \yabox|1/2 max| (
        indicates the half-maximum point of \yabox|target|)
        \item \yabox|target| (required, string): The target for the ignition
        \yabox|type| measurement; one of \yabox|temperature|, \yabox|pressure|,
        \yabox|OH|, \yabox|OH*|, \yabox|CH|, or \yabox|CH*|
    \end{itemize}
\end{itemize}

>>>>

However, ReSpecTh experimental files are another
XML-based format, and, as such, suffer from the same readability issues as PrIMe.
Moreover, the standard remains inaccessible to the public, requiring potential users
to register with the standard's authors using a valid institutional email address
to access the specification and the growing database.

@@

The second section of the file encodes the experimental data. The \ck{} file
describes these using a sequence of mappings, with the following information required
in each element of the sequence:
%
\begin{itemize}
    \item \yabox|temperature| (required, sequence): The temperature of the
    experiment, with units and optionally uncertainty
    \item \yabox|ignition-delay| (required, sequence): The ignition delay of the
    experiment, with units and optionally uncertainty
    \item \yabox|pressure| (required, sequence): The pressure of the experiment,
    with units and optionally uncertainty
    \item \yabox|composition| (required, mapping): The composition of the
    mixture in the experiment, described via a nested mapping with the fields
    \begin{itemize}
        \item \yabox|kind| (required, string): one of \yabox|mole fraction|, \yabox|mole percent|, or \yabox|mass fraction|
        \item \yabox|species|: sequence of mappings, with the fields
        \begin{itemize}
            \item \yabox|species-name| (required, string): The name of the species
            \item \yabox|amount| (required, sequence): The mole fraction or percent, or the mass fraction, optionally with uncertainty
            \item \yabox|InChI|, \yabox|SMILES|, \yabox|atomic-composition|, or
            \yabox|elemental-composition| (required, string or sequence): The InChI
            or SMILES string representing the molecule, or its atomic or elemental
            composition (\yabox|atomic-composition| and\\
            \yabox|elemental-composition| are synonyms) as a sequence
        \end{itemize}
    \end{itemize}
    \item \yabox|ignition-type| (required, mapping): The method used to detect
    ignition in the experiments. The required fields are
    \begin{itemize}
        \item \yabox|type| (required, string): How ignition delay was
        measured; one of \yabox|d/dt max| (indicates the ignition point was
        found at the maximum of the time derivative of the \yabox|target|),
        \yabox|max| or \yabox|min| (indicates the ignition point was at the
        maximum or minimum of the \yabox|target|), \yabox|1/2 max| (
        indicates the half-maximum point of \yabox|target|), or \yabox|d/dt max extrapolated|
        (indicates the maximum slope of the target extrapolated to the baseline)
        \item \yabox|target| (required, string): The target for the ignition
        \yabox|type| measurement; one of \yabox|temperature|, \yabox|pressure|,
        \yabox|OH|, \yabox|OH*|, \yabox|CH|, or \yabox|CH*|
    \end{itemize}
\end{itemize}
